% Aquí va la Bibliografía utilizada por el proyecto.
\begin{thebibliography}{15}

% Calibración y contenido del detector de Harris
\bibitem{FAUG93}
Faugeras, Olivier, \emph{Three-Dimensional Computer Vision} The MIT Press.
(1993).

\bibitem{FAUG01}
Faugeras, Olivier and Quang-Tuan Luong and Theo Papadopoulo,
\emph{The geometric of multiples images: the law that govern the formation of multiple
images of a scene and some of their applications} The MIT Press.
(2001).

\bibitem{KANA95}
Kenichi Kanatani, \emph{Geometric Computation for Machine Vision} Oxford University Press.
(1995).

\bibitem{HART01}
Richard Hartley and Andrew Zisserman, \emph{Multiple View Geometry in Computer Vision} The MIT Press.
(2001).

\bibitem{ALVA01}
Alvarez, Luis and Cuenca, Carmelo and Mazorra, Luis, \emph{Signal Processing, Pattern Recognition
and Applications. IASTED.} Morphological Corner Detector. Application to Camera Calibration.
(2001).


% Ingenieria del Software
\bibitem{PRE01}
Roger S. Pressman, \emph{Ingeniería del Software, quinta edición} McGraw-Hill Companies.
(2001).

\bibitem{GAM94}
Erich Gamma, Richard Helm, Ralph Johnson and John Vlissides, \emph{Design Patterns} Addison Wesley Publishing Company.
(1994).


% Programación
\bibitem{HEI98}
Gregory L. Heileman, \emph{Estructuras de datos, algoritmos y programación orientada a objetos.}
McGraw-Hill/Interamericana de España S.A.U. 1998.

\bibitem{MEY97}
Scott Meyers, \emph{Effective C++} Addison Wesley Publishing Company.
(1997).

\bibitem{WER94:1}
Josie Wernecke, \emph{The Inventor Mentor} Addison Wesley Publishing Company.
(1994).

\bibitem{WER94:2}
Josie Wernecke, \emph{The Inventor Toolmaker} Addison Wesley Publishing Company.
(1994).

\bibitem{WRI97}
Richard S. Wright Jr., \emph{Programación en OpenGL} Anaya Multimedia.
(1997).


% UML
\bibitem{BOO00}
Grady Booch, James Rumbaugh and Ivar Jacobson, \emph{El lenguaje unificado de modelado} Addison Wesley Publishing Company.
(2000).

\bibitem{FOW97}
Martin Fowler and Kendall Scott, \emph{UML gota a gota} Addison Wesley Publishing Company.
(1997).


% Documentación
\bibitem{DIL93}
Antoni Diller, \emph{Latex line by line} Wiley Professional Computing.
(1993).


\end{thebibliography}
